# Assignment resources

```{r echo=FALSE}
library(knitr)
```


Listed below are some helpful books, datasets and tools you might find useful when completing your assignments.

## Books/reading resources

There are a lot of free online books for geospatial analysis, especially using R, check out:

* https://www.rstudio.com/resources/training/books/
* http://hadley.nz/
* https://geocompr.robinlovelace.net/
* https://happygitwithr.com/

## New developments

Every year there is a useR conference that provides a load to tutorials on the latest developments and research...check them out here: http://www.user2019.fr/tutorials/ and here: https://github.com/sowla/useR2019-materials

## Data

This is by no means an extensive data list, but summarises data used within all the practicals alondside a few additions that you might want to explore when sourcing data for your assignments. You are by no means limited to these data sets, so go and explore...

* UK data service: https://census.edina.ac.uk/
* ONS: https://www.ons.gov.uk/
* Edina (e.g. OS mastermap): https://digimap.edina.ac.uk/
* Open Topography: https://opentopography.org/
* USGS Earth Explorer: https://earthexplorer.usgs.gov/
* Geofabrik (OSM data): https://www.geofabrik.de/
* Global weather data (points): https://rp5.ru/Weather_in_the_world
* London data store: https://data.london.gov.uk/
* Air b n b data: http://insideairbnb.com/get-the-data.html
* NASA SocioEconomic Data and Applications Center (SEDAC): https://sedac.ciesin.columbia.edu/
* UN environmental data explorer: http://geodata.grid.unep.ch/
* World pop: https://www.worldpop.org/
* DIVA-GIS: https://www.diva-gis.org/
* DEFRA: https://environment.data.gov.uk/
* US Cesus data: https://www.census.gov/data.html
* TFL open data: https://tfl.gov.uk/info-for/open-data-users/our-open-data?intcmp=3671#on-this-page-2
* EU tourism data: https://ec.europa.eu/eurostat/statistics-explained/index.php/Tourism_statistics
* NASA EARTHDATA: https://earthdata.nasa.gov/

## Data lists

Awesome public datasets have a wide range all data (some geographic, some not): https://github.com/awesomedata/awesome-public-datasets

Robin Wilson has authored one of the most extensive data lists that i've come across: https://freegisdata.rtwilson.com/

## Critically reading and writing

Hugh Kerans from Flinders Unversity, Adelaide has developed a range of materials to assist graduate students in producing effective reports and publications...check out his website and resouces here: https://www.ithinkwell.com.au/

The most useful templates for the assignments are the critical reading one:

```{r echo=FALSE, out.height = "600pt", out.width = "800pt", cache=TRUE}
include_graphics('assignment/CriticalReading.pdf', auto_pdf = getOption("knitr.graphics.auto_pdf", FALSE)
)
```

and questions to ask as you write a paper (or assignment):

```{r echo=FALSE, out.height = "600pt", out.width = "800pt", cache=TRUE}
include_graphics('assignment/QuestionsToAskAsYouWriteAPaper.pdf', auto_pdf = getOption("knitr.graphics.auto_pdf", FALSE)
)
```

You can download these from this website directly, my GitHub or Hugh's website.

Sven Åke Bjørke from the University of Agder also produced a few Youtube videos on academic writing and critical thinking that might be useful...

```{r echo=FALSE, fig.align='center', cache=TRUE}
knitr::include_url("https://www.youtube.com/embed/1NGMoW51jmA")
```

## Free flow diagram tools

* PowerPoint (from UCL software site)
* Draw.io: https://www.draw.io/ 
* Lucidchart: https://www.lucidchart.com/pages/examples/flowchart-maker

Free at the time of writing