# Assignment resources

```{r echo=FALSE}
library(knitr)
```

Listed below are some helpful website, books, datasets and tools you might find useful when completing your assignments.

## Timeline

There is a suggested timeline of work for your assignment provided in the assessment requirements document on Moodle. 

## Markscheme

The markscheme can be found on Moodle with a break down of how much percent is given to each criteron.  

## Examples of previous work

Closer to the assignment deadline we will release examples of good student projects from previous years as a tab on Moodle.

## Cool stuff to explore

New packages and functions that i've recently come across that are worth exploring..

* RStudio cloud: https://rstudio.cloud/ --- like RStudio but online, great for collaborating
* Animating plots: https://rpubs.com/jgleeson/ripple-effect
* Bivariate maps: https://timogrossenbacher.ch/2019/04/bivariate-maps-with-ggplot2-and-sf/
* Rayshader: https://www.rayshader.com/
* Cartography package: http://riatelab.github.io/cartography/docs/

## Books/reading resources

There are a lot of free online books for geospatial analysis, especially using R, check out:

* https://www.rstudio.com/resources/training/books/
* https://r-graphics.org/
* http://hadley.nz/
* https://geocompr.robinlovelace.net/
* https://happygitwithr.com/
* https://bookdown.org/
* https://plotly-r.com/index.html
* https://bookdown.org/ndphillips/YaRrr/
* https://thinkr-open.github.io/building-shiny-apps-workflow/

If you want to produce more efficent R code then have a look at the [Efficient R programming](https://csgillespie.github.io/efficientR/index.html) book.

## New developments

Every year there is a useR conference that provides a load to tutorials on the latest developments and research...check them out here: 

* http://www.user2019.fr/tutorials/
* https://github.com/sowla/useR2019-materials

Other useful tutorials can be found here:

* http://rpubs.com/chrisbrunsdon/
* http://rpubs.com/alexsingleton/
* https://mgimond.github.io/megug2017/#cropping-a-raster-interactively

### Twitter

R package authors regular tweet with updates and new developments. If twitter is your thing go and follow these people to start with:

* [Hadley Wickham](https://twitter.com/hadleywickham)
* [Alison Hill](https://twitter.com/apreshill)
* [Robin Lovelace](https://twitter.com/robinlovelace)
* [Yihui Xie](https://twitter.com/xieyihui)
* [Hannah Frick](https://twitter.com/hfcfrick)
* [Jakub Nowosad](https://twitter.com/jakub_nowosad)

and anyone else you come across...

## Data

This is by no means an extensive data list, but summarises data used within some of the practicals alongside a few additions that you might want to explore when sourcing data for your assignments. You are **not limited** to these data sets for you assessment.

* US City Open Data Census: http://us-cities.survey.okfn.org/
* nomis: https://www.nomisweb.co.uk/
* ONS geoportal: https://geoportal.statistics.gov.uk/
* UK data service: https://census.edina.ac.uk/
* ONS: https://www.ons.gov.uk/
* Edina (e.g. OS mastermap): https://digimap.edina.ac.uk/
* Open Topography: https://opentopography.org/
* USGS Earth Explorer: https://earthexplorer.usgs.gov/
* Geofabrik (OSM data): https://www.geofabrik.de/
* Global weather data (points): https://rp5.ru/Weather_in_the_world
* London data store: https://data.london.gov.uk/
* Air b n b data: http://insideairbnb.com/get-the-data.html
* NASA SocioEconomic Data and Applications Center (SEDAC): https://sedac.ciesin.columbia.edu/
* UN environmental data explorer: http://geodata.grid.unep.ch/
* World pop: https://www.worldpop.org/
* DIVA-GIS: https://www.diva-gis.org/
* DEFRA: https://environment.data.gov.uk/
* US Cesus data: https://www.census.gov/data.html
* TFL open data: https://tfl.gov.uk/info-for/open-data-users/our-open-data?intcmp=3671#on-this-page-2
* TFL cycling data: https://cycling.data.tfl.gov.uk/
* EU tourism data: https://ec.europa.eu/eurostat/statistics-explained/index.php/Tourism_statistics
* NASA EARTHDATA: https://earthdata.nasa.gov/
* Camden air action: https://camdenairaction.wordpress.com/2017/02/20/schools-monitoring-project-spring-2017/
* Kings data on air pollution: https://www.londonair.org.uk/LondonAir/Default.aspx
* Uber travel time data: https://movement.uber.com/?lang=en-GB
* Eurostat: https://ec.europa.eu/eurostat

## Data lists

Awesome public datasets have a wide range all data (some geographic, some not): https://github.com/awesomedata/awesome-public-datasets

Robin Wilson has authored one of the most extensive data lists that i've come across: https://freegisdata.rtwilson.com/

## Reading and writing critically

Hugh Kerans from Flinders Unversity, Adelaide has developed a range of materials to assist graduate students in producing effective reports and publications...check out his website and resouces here: https://www.ithinkwell.com.au/

The most useful templates for the assignments are the critical reading one:

```{r echo=FALSE, out.height = "600pt", out.width = "800pt", cache=TRUE}
include_graphics('assignment/CriticalReading.pdf', auto_pdf = getOption("knitr.graphics.auto_pdf", FALSE)
)
```

and questions to ask as you write a paper (or assignment):

```{r echo=FALSE, out.height = "600pt", out.width = "800pt", cache=TRUE}
include_graphics('assignment/QuestionsToAskAsYouWriteAPaper.pdf', auto_pdf = getOption("knitr.graphics.auto_pdf", FALSE)
)
```

You can download these from this website directly, my GitHub or Hugh's website.

Sven Åke Bjørke from the University of Agder also produced a few Youtube videos on academic writing and critical thinking that might be useful...

```{r echo=FALSE, fig.align='center', cache=TRUE}
knitr::include_url("https://www.youtube.com/embed/1NGMoW51jmA")
```

...And the paper ['How to write a paper for publicaiton'](https://onlinelibrary.wiley.com/doi/full/10.1046/j.1444-2892.2000.00031.x)

## Free flow diagram tools

* PowerPoint (from UCL software site)
* Draw.io: https://www.draw.io/ 
* Lucidchart: https://www.lucidchart.com/pages/examples/flowchart-maker

Free at the time of writing