--- 
title: "CASA0005 Geographic Information Systems and Science"
author: "Andy MacLachlan and Adam Dennett"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
#github-repo: rstudio/bookdown-demo
description: ""
---

# Welcome {-}

Welcome to the CASA0005 Geographic Information Systems and Science online pratical handbook. This website is hosted on GitHub and holds all the practical instructions and data. All data used within the practicals is available online, however occasionally websites can undergo maintenance or be inaccessible due to political factors such as government shutdowns.  

If you need the practical data you can access it from my github repository here: https://github.com/andrewmaclachlan/CASA0005repo

Practical data is divided into the relevant sessions, although sometimes i'll refer to a dataset used within a previous week. 

## The world of GIS {-}

Spatial analysis can yield fascinating insights into geographical relationships. However, at times it can be difficult to work with. You will get lots of error messages and have software crash. The academic staff are here to help you work through these practicals but we do not know everything. It's a good idea to become familar with online sources of help, such as:

* Stack Exchange https://stackexchange.com/
* RStudio community https://community.rstudio.com/
* QGIS documemtation https://docs.qgis.org/3.4/en/docs/index.html
* R documentation https://www.rdocumentation.org/
* ArcGIS help pages https://support.esri.com/en

Want to see what you can do with spatial analysis...check out this 'What's Next' video produced for the ESRI conference...

```{r echo=FALSE, fig.align='center', cache=TRUE}
knitr::include_url("https://www.youtube.com/K0qZffiKwak")
```

## Getting started {-}

One of the issues with GIS is that many of the files we will be working with are quite large. Fortunately in recent years UCL has seriously beefed up the storage available for students. You now get 100GB of free storage, which should be plenty for the work you will be doing this year! The Bartlett faculty has several gigabytes of storage space available on their central servers, so before we get started, we will connect to our N drive to carry out all of our practical work over the coming weeks. 

## Offline viewing {-}

The best way to view this practical book is through the website. However if you are unable to access the internet you can either download the ```.epub``` book or save specific webpages for offline viewing --- note that any interactive plots won't work in the ```.epub``` book. As this is a live document if you select to download the ```.epub``` make sure you redownload it regularly to keep up to date with any changes to the material. Insturctions for Google Chrome are provided here: https://support.google.com/chrome/answer/7343019?co=GENIE.Platform%3DDesktop&hl=en&oco=1

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```

## More help {-}

If you need specific assistance with this course please:

* Check the module handbook for queries relating to assignments / deadlines 
* Speak to a member of the teaching team in the computer lab sessions
* Ask a question at the end of a lecture (time permitting)
* Ask a question on slack

Due to the size of the class we will only reply to messages on slack so all students can see the discussion.

If after persuing all these avenues you still need help you can book into our office hours are specified below. These meetings are **to discuss a geographical concept in relation to the material/assignments or for any personal matters relevant to the completion of the course**. 

These meetings are **not** to be used for specific technical issues. Problems of this nature should be addressed in the practical sessions.

Andy: https://amaclachlan.youcanbook.me/ 

Adam: https://dr-d-casa.youcanbook.me

## Noticed a mistake? {-}

No one is perfect, if you notice a mistake let us know through the GitHub issues tab...

https://github.com/andrewmaclachlan/CASA0005repo/issues

Don't worry if you are unsure about what GitHub is we cover it in the course.

## Assignment resources {-}

Want some tips for resources on your assignment?.... head over to the [Assignment resources] pages
